Pesticides in small agricultural streams in Germany

### 2016-08-19 cover_letter/cover.tex
cover letter + refs

\usepackage{graphicx} % Required for including pictures
\usepackage{microtype} % Improves typography
\usepackage[T1]{fontenc} % Required for accented characters
\usepackage[utf8]{inputenc}

@@

\textwidth 6.75in
\textheight 9.25in
\oddsidemargin -.25in
\evensidemargin -.25in
\topmargin -1in
\parindent 0.4in

@@

\address{
    \hspace{\fill}\includegraphics[width=3in]{Uni-Logo-2c.jpg} % Include the logo 
    ~\\[-0.11in] % Reduce the whitespace above the horizontal rule
    \vhrulefill{1pt} \\ 
    \hspace{\fill}\parbox[t]{4in}{ % Create a box for your details underneath the horizontal rule on the right
        \vspace{0.6in}
        \textbf{\Who} \em \\ % Your name, all text after this will be italicized
        \Where\\ % Your department
        \Address\\ % Your address
        \CityZip\\ % Your city and zip code
        \TEL\\ % Your phone number
        \Email\\ % Your email address
    }
    \hspace{-1.4in} % Horizontal position of this block, increase to move left, decrease to move right
    \vspace{-1in} % Move the letter content up for a more compact look
}

@@

\def\opening#1{
\thispagestyle{empty}
{\centering\fromaddress \vspace{1in} \\} 
{\raggedright \toname \\ \toaddress \par} % Print the to name and address
\vspace{2em}
% Subject line
\noindent
\textbf{Subject line} \hspace*{\fill}\today \\[2em]
\vspace{0.6in} % White space after the to address
\noindent #1 % Print the opening line
}

@@

@@

\opening{Dear editor of Environmental Science \& Technology,}

xxxxx

\closing{Sincerely, }

>>>>

\usepackage{graphicx} % Required for including pictures
\usepackage[T1]{fontenc} % Required for accented characters
\usepackage[utf8]{inputenc}

@@

\textwidth 6.75in
\textheight 9.25in
\oddsidemargin -.25in
\evensidemargin -.25in
\topmargin -1.5in
\parindent 0in

@@

\address{
    % Include the logos
    \includegraphics[width=3in]{Uni-Logo-2c.jpg}\hspace{\fill}\includegraphics[width=2in]{logo_institut.jpg}
    ~\\[-0.11in] % Reduce the whitespace above the horizontal rule
    \vhrulefill{1pt} \\ 
    \hspace{\fill}\parbox[t]{4in}{ % Create a box for your details underneath the horizontal rule on the right
        \vspace{0.2in}
        \textbf{\Who} \em \\ % Your name, all text after this will be italicized
        \Where\\ % Your department
        \Address\\ % Your address
        \CityZip\\ % Your city and zip code
        \TEL\\ % Your phone number
        \Email\\ % Your email address
    }
    \hspace{-1.4in} % Horizontal position of this block, increase to move left, decrease to move right
    \vspace{-1in} % Move the letter content up for a more compact look
}

@@

\def\opening#1{
\thispagestyle{empty}
{\centering\fromaddress \vspace{0.5in} \\} 
{\raggedright \toname \\ \toaddress \par} % Print the to name and address
\vspace{2em}
% Subject line
\noindent
\textbf{Submission of article} \hspace*{\fill}\today \\[2em]
\vspace{0.6in} % White space after the to address
\noindent #1 % Print the opening line
}

@@

% noindent
\setlength\parindent{0pt}

@@

\opening{Dear Editor,}
\vspace{-1em}\\
enclosed is a manuscript to be considered for publication in Environmental Science \& Technology titled \\

\emph{Pesticides in small agricultural streams in Germany}\\

Pesticides enter freshwater ecosystems from agricultural areas and may have effects on biota.
However, relatively little is know about their large-scale distribution.
Especially, small streams may be at high risk because of adjacency to fields and small water columns.

We compiled and homogenized monitoring data from all German Federal States with a focus on small to mid-size streams. 
Our results show that there is lack of knowledge for small streams. 
However, the data revealed the pesticides are commonly occurring.
Especially, neonicotinoid pesticides may pose a risk to small agricultural freshwaters.

Our study should be of general interest and add valuable information on chemical monitoring, pesticide occurrences and ecological risk arising from them.

If you have any further questions do not hesitate to contact me.

\closing{Yours sincerely, }
